# Parts

You can add parts to organize one or more book chapters together. Parts can be inserted at the top of an .Rmd file, before the first-level chapter heading in that same file. 

Add a numbered part: `# (PART) Act one {-}` (followed by `# A chapter`)

Add an unnumbered part: `# (PART\*) Act one {-}` (followed by `# A chapter`)

Add an appendix as a special kind of un-numbered part: `# (APPENDIX) Other stuff {-}` (followed by `# A chapter`). Chapters in an appendix are prepended with letters instead of numbers.

## `timevis` Timelines

```{r}
timevisData <- data.frame(
  id = 1:11,
  content = c("Open", "Open",
              "Open", "Open", "Half price entry",
              "Staff meeting", "Open", "Adults only", "Open", "Hot tub closes",
              "Siesta"),
  title = c(""),
  start = c("2016-05-01 07:30:00", "2016-05-01 14:00:00",
            "2016-05-01 06:00:00", "2016-05-01 14:00:00", "2016-05-01 08:00:00",
            "2016-05-01 08:00:00", "2016-05-01 08:30:00", "2016-05-01 14:00:00",
            "2016-05-01 16:00:00", "2016-05-01 19:30:00",
            "2016-05-01 12:00:00"),
  end   = c("2016-05-01 12:00:00", "2016-05-01 20:00:00",
            "2016-05-01 12:00:00", "2016-05-01 22:00:00", "2016-05-01 10:00:00",
            "2016-05-01 08:30:00", "2016-05-01 12:00:00", "2016-05-01 16:00:00",
            "2016-05-01 20:00:00", NA,
            "2016-05-01 14:00:00"),
  group = c(rep("lib", 2), rep("gym", 3), rep("pool", 5), NA),
  type = c(rep("range", 9), "point", "background")
)
timevisDataGroups <- data.frame(
  id = c("lib", "gym", "pool"),
  content = c("Library", "Gym", "Pool")
)
```


```{r}
timevis::timevis(data = timevisData,
                 groups = timevisDataGroups) %>%
  timevis::centerItem(itemId = 8) %>%
  timevis::setWindow(start = "2016-05-01 01:00:00", 
                      end = "2016-05-01 23:00:00
")
```

