# Risk Register

## High Risks
High risk items are assessed with high Efficacy, Cost, or Schedule risk. 

```{r high-risk, echo=FALSE, warning=FALSE, message=FALSE}
risk_high <- filter(risk, COST_RISK == "HIGH" | 
                          SCHEDULE_RISK == "High" |
                          EFFICACY_RISK == "High")
```

```{r echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=2, out.width='100%'}
risk_pies(risk_high)
```

```{r high-risk-register-table, echo=FALSE, warning=FALSE, message=FALSE}
risk_register_table(risk_high)
```

## Open Risks
Risk items are considered "open" if they are still highly relevant for ongoing team consideration (Status = Open). 
```{r echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=2, out.width='100%'}
risk_pies(filter(risk, MANAGEMENT_STATUS == "Open"))
```

```{r open-risk-table, echo=FALSE, warning=FALSE, message=FALSE}
risk_register_table(filter(risk, MANAGEMENT_STATUS == "Open"))
```

```{r download-risk, echo=FALSE, warning=FALSE, message=FALSE}
risk %>%
  download_file(path = "download/risk.csv",
                output_name = "risk",
                button_label = "Download data",
                button_type = "warning",
                has_icon = FALSE)
```

## Closed Risks
Risk items are considered "closed" if they are no longer highly relevant for ongoing team consideration (Status = Closed). 
```{r closed-risk-table, echo=FALSE, warning=FALSE, message=FALSE}
risk_register_table(filter(risk, MANAGEMENT_STATUS == "Closed"))
```


## Related Items
```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
# Create hierarchical edge bundle plot
edgebundleR::edgebundle(relate_igraph, 
                        tension = 0.8, 
                        fontsize = 12,
                        padding = 60)
```


```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Cohesive Blocks Related Items"}
related_blocks_table(related_blocks)
```


## Summary Statistics
```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=9, out.width='100%', fig.cap = paste0("Risk Characteristics (n = ", length(unique(risk$RISK_NO)), ")")}
p1 <- percent_treemap(risk, RISKCATEGORY, "Risk Categories")
p2 <- percent_treemap(risk, FEATURE, "Project Features")
p3 <- percent_treemap(risk, RISK_STRATEGY, "Risk Strategy")
p4 <- percent_treemap(risk, TIMING_OF_DELAY, "Timing of Delay")
p5 <- percent_treemap(risk, DISCIPLINE, "Discpline")
grid.arrange(p1, p2, p3, p4, p5, nrow = 3, ncol = 2)
```

## Project Timeline
```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Project Timeline"}
timeline(risk_df = risk_time, 
         groups_df = risk_time_riskcategory,
         height = "700px",
         start = "2021-01-01",
         end = "2025-01-01")
```
