--- 
title: "Brandon Road Interbasin Project Risk Analysis Report"
author: "USACE Rock Island District"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
description: "Report description goes here."
bibliography: [book.bib, packages.bib]
biblio-style: apalike
csl: chicago-fullnote-bibliography.csl
---

# Introduction {-}

## Project 
* P2 project name: Brandon Rd-Great Lakes/Miss Rvr Interbasin
* P2 project number: 482782
* P2 program code: 451617

## Architecture
This report using the following architecture:  

* **Data Entry** - An [Oracle APEX](https://apex.oracle.com/) web-database application stores the risk analysis data and allows project risk managers to enter and edit the data. This application resides on the USACE intranet (CorpsNet) and is only available for editing to project risk managers.  
* **Reporting** - This report is produced using [R]()  
* **Code Repository** -   
* **Static Website Publishing** -   
* **Project Viewer** -   

```{r, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.cap="Report Architecture"}
knitr::include_graphics(path = "diagrams/cloud_arch-workflow.drawio.svg")
```


<!-- Libraries -->
```{r library, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(knitr)
library(rmarkdown)
library(rlang)
library(lubridate)
library(DBI)
library(ROracle)
library(keyring)
library(tools)
library(kableExtra)
library(pander)
library(timevis)
library(treemapify)
library(gridExtra)
library(formattable)
library(igraph)
```

```{r source, echo=FALSE, warning=FALSE, message=FALSE}
source("R/risk_register_table.R")
source("R/decision_register_table.R")
source("R/action_register_table.R")
source("R/atx_header.R")
source("R/pandoc_header.R")
source("R/percent_treemap.R")
source("R/timeline.R")
source("R/format_id.R")
source("R/id_link.R")
source("R/eng_level_history.R")
source("R/discussion_table.R")
source("R/related_block_table.R")
source("R/remove_test_records.R")
source("R/convert_date.R")
source("R/impact_outcome_table.R")
```


```{r, echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}
# Manually export all views from MVR egis-db BrandonRoad to the data folder
# Not needed if connecting directly to db (see below)

# Cleanup file names from Oracle export
data_files_oracle <- list.files("data")
data_files <- str_remove(data_files_oracle, "_DATA_VIEW")
file.rename(from = paste0("data/", data_files_oracle),
            to = paste0("data/", data_files))

# Import Oracle tables
risk_oracle              <- read_csv("data/RISK_MAIN_VIEW.csv")
events_oracle            <- read_csv("data/EVENTS_MAIN_VIEW.csv")
discussion_oracle        <- read_csv("data/DISCUSSION_LOG_MAIN_VIEW.csv")
action_oracle            <- read_csv("data/ACTION_MAIN_VIEW.csv")
decision_oracle          <- read_csv("data/DECISION_MAIN_VIEW.csv")

rel_action_action_oracle <- read_csv("data/REL_ACTION_ACTION_MAIN_VIEW.csv")
rel_dec_dec_oracle       <- read_csv("data/REL_DEC_DEC_MAIN_VIEW.csv")
rel_dec_action_oracle    <- read_csv("data/REL_DEC_ACTION_MAIN_VIEW.csv")
rel_risk_action_oracle   <- read_csv("data/REL_RISK_ACTION_MAIN_VIEW.csv")
rel_risk_dec_oracle      <- read_csv("data/REL_RISK_DEC_MAIN_VIEW.csv")
rel_risk_risk_oracle     <- read_csv("data/REL_RISK_RISK_MAIN_VIEW.csv")

# Convert date fields to POSITct
risk_oracle       <- convert_date(risk_oracle)
events_oracle     <- convert_date(events_oracle)
discussion_oracle <- convert_date(discussion_oracle)
action_oracle     <- convert_date(action_oracle)
decision_oracle   <- convert_date(decision_oracle)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Use the `keyring` package to save the database username and password in the 
# system credential store
key_service <- "egis-db-brandonroad"
user_name <- "BrandonRoad"
# Set once on each computer prior to building book
#keyring::key_set(service = key_service, username = user_name)

# Make Oracle connection
drv  <- DBI::dbDriver("Oracle")
host <- "egis-db"
port <- "1521"
sid  <- "B5SDEDP1"
connect_string <- paste0(
  "(DESCRIPTION=",
  "(ADDRESS=(PROTOCOL=tcp)(HOST=", host, ")(PORT=", port, "))",
  "(CONNECT_DATA=(SID=", sid, ")))")
 
con_roracle <- ROracle::dbConnect(drv, 
                                  username = user_name, 
                                  password = key_get(key_service, user_name),
                                  dbname   = connect_string)
```


```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Import tables from Oracle
risk_oracle              <- ROracle::dbReadTable(con_roracle, 
                                                 "RISK_MAIN_VIEW")
events_oracle            <- ROracle::dbReadTable(con_roracle, 
                                                 "EVENTS_MAIN_VIEW")
discussion_oracle        <- ROracle::dbReadTable(con_roracle, 
                                                 "DISCUSSION_LOG_MAIN_VIEW")
action_oracle            <- ROracle::dbReadTable(con_roracle, 
                                                 "ACTION_MAIN_VIEW")
decision_oracle          <- ROracle::dbReadTable(con_roracle, 
                                                 "DECISION_MAIN_VIEW")
rel_action_action_oracle <- ROracle::dbReadTable(con_roracle, 
                                                 "REL_ACTION_ACTION_MAIN_VIEW")
rel_dec_dec_oracle       <- ROracle::dbReadTable(con_roracle, 
                                                 "REL_DEC_DEC_MAIN_VIEW")
rel_dec_action_oracle    <- ROracle::dbReadTable(con_roracle, 
                                                 "REL_DEC_ACTION_MAIN_VIEW")
rel_risk_action_oracle   <- ROracle::dbReadTable(con_roracle, 
                                                 "REL_RISK_ACTION_MAIN_VIEW")
rel_risk_dec_oracle      <- ROracle::dbReadTable(con_roracle, 
                                                 "REL_RISK_DEC_MAIN_VIEW")
rel_risk_risk_oracle     <- ROracle::dbReadTable(con_roracle, 
                                                 "REL_RISK_RISK_MAIN_VIEW")

# Disconnect from the database
ROracle::dbDisconnect(con_roracle)
```


<!-- Report Constants -->
```{r, echo=FALSE, warning=FALSE, message=FALSE}
qa_email_address <- "Marisa.C.Lack@usace.army.mil"
current_date <- lubridate::today()
```


<!-- Wrangle Risk/Action/Decision Data -->
```{r wrangle-risk, echo=FALSE, warning=FALSE, message=FALSE}
# Filter for "Active" records
risk <- risk_oracle %>%
  filter(ACTIVE == "Yes")

# Remove test data
risk <- remove_test_records(risk, "RISK_NO")

# Rename date fields
risk <- risk %>%
  rename_with(.fn = str_to_lower, 
              .cols = ends_with("_date"))

# Process assessment fields
risk <- risk %>%
  rename(cost_risk_color     = CONDITIONAL_FORMATTING,
         schedule_risk_color = CONDITIONAL_FORMATTING2,
         efficacy_risk_color = CONDITIONAL_FORMATTING3) %>%
  mutate(cost_risk_color     = tolower(cost_risk_color),
         schedule_risk_color = tolower(schedule_risk_color),
         efficacy_risk_color = tolower(efficacy_risk_color))

# Set engagement level integer, risk_cat_code
risk <- risk %>%
  mutate(eng_level = as.numeric(str_extract(ENG_LEVEL, "\\d")),
         risk_cat_code = str_extract(RISK_NO, "\\w+\\b"))

# Add efficacy_impact_per_project (not applicable, so set blank)
risk$EFFICACY_IMPACT_PER_PROJECT <- ""

# Convert factor variables to title case for labeling
risk$RISKCATEGORY <- toTitleCase(tolower(risk$RISKCATEGORY))

# Cleanup risk number for sorting
risk <- format_id(risk, "RISK_NO")

# Remove unused fields
risk <- risk %>%
  select(!c(PDT_DISC_CONC, PDT_DISC_LIKELI_IMPACT,
            PDT_DISC_RISK_MANAG_STRATEGY, ACTION_ITEMS, LESSONS_LEARNED,
            FK_TABLE_ID))

# Create hyperlink to risk_no
risk <- id_link(risk, "risk_no")

# Reorder fields
risk <- risk %>%
  relocate(risk_no, .after = RISK_NO) %>%
  relocate(risk_no_link, .after = risk_no) %>%
  relocate(CONCERNS, .after = risk_no_link) %>%
  relocate(COST_RISK, .after = COST_IMPACT_PER_PROJECT) %>%
  relocate(cost_risk_color,  .after = COST_RISK) %>%
  relocate(SCHEDULE_RISK, .after = SCHEDULE_IMPACT_PER_PROJECT) %>%
  relocate(schedule_risk_color, .after = SCHEDULE_RISK) %>%
  relocate(EFFICACY_IMPACT, .after = EFFICACY_LIKELIHOOD) %>%
  relocate(EFFICACY_IMPACT_PER_PROJECT, .after = EFFICACY_IMPACT) %>%
  relocate(efficacy_risk_color, .after = EFFICACY_RISK) %>%
  relocate(TIMING_OF_DELAY, .after = RISK_STRATEGY) %>%
  relocate(start_date, .after = CONCERNS) %>%
  relocate(end_date, .after = start_date) %>%
  relocate(poc_review_date, .after = TECHNICAL_POC) %>%
  relocate(eng_level, .after = ENG_LEVEL) %>%
  relocate(risk_cat_code, .after = RISKCATEGORY)

# Remove duplicates and sort
risk <- risk %>%
  arrange(risk_no, desc(level_date)) %>%                  # get the latest level
  distinct(risk_no, .keep_all = TRUE)

# Cleanup
#rm(risk_oracle)
```

```{r wrangle-events, echo=FALSE, warning=FALSE, message=FALSE}
# Remove test records
events <- remove_test_records(events_oracle, "FK_TABLE_ID") 

# Rename date fields
events <- events %>%
  rename_with(.fn = str_to_lower, 
              .cols = ends_with("_date"))

# Set engagement level integer field
events <- events %>%
  mutate(eng_level = as.numeric(str_extract(ENG_LEVEL, "\\d")))

# Cleanup risk number for sorting
events <- format_id(events, "FK_TABLE_ID")

# Remove unused fields
events <- events %>%
  select(!c(CREATED_USER, LAST_EDITED_USER))

# Create hyperlink to fk_table_id
events <- id_link(events, "fk_table_id")

# Reorder fields
events <- events %>%
  relocate(fk_table_id, .after = FK_TABLE_ID) %>%
  relocate(fk_table_id_link, .after = fk_table_id) %>%
  relocate(DESCRIPTION, .after = fk_table_id_link) %>%
  relocate(level_date, .after = ENG_LEVEL) %>%
  relocate(eng_level, .after = ENG_LEVEL)

# Sort
events <- events %>%
  arrange(TABLE_NAME, fk_table_id, as.Date(level_date))

# Calc event duration (days) within item types (risk/action/decision) and items
events <- events %>% 
  group_by(TABLE_NAME, fk_table_id) %>%
  mutate(level_end_date = lead(as.Date(level_date), n = 1, 
                               default = current_date),
         date_interval = lubridate::interval(as.Date(level_date), 
                                             level_end_date),
         duration_days = lubridate::time_length(date_interval, 
                                                unit = "days")) %>%
  ungroup(TABLE_NAME, fk_table_id)

# Cleanup
#rm(events_oracle)
```

```{r wrangle-discussion, echo=FALSE, warning=FALSE, message=FALSE}
# Remove test records
discussion <- remove_test_records(discussion_oracle, "FK_TABLE_ID")

# Rename date fields
discussion <- discussion %>%
  rename_with(.fn = str_to_lower, 
              .cols = ends_with("_date"))

# Cleanup discussion number for sorting
discussion <- format_id(discussion, "FK_TABLE_ID")

# Remove unused fields
discussion <- discussion %>%
  select(!c(LOGGED_BY, CREATED_USER, LAST_EDITED_USER, ACTIVE))

# Reorder fields
discussion <- discussion %>%
  relocate(fk_table_id, .after = FK_TABLE_ID) %>%
  relocate(RESPONSIBLE_POC, .after = DISCUSSION) %>%
  relocate(poc_review_date, .after = RESPONSIBLE_POC)

# Cleanup
#rm(discussion_oracle)
```

```{r wrangle-action, echo=FALSE, warning=FALSE, message=FALSE}
# Remove test records
action <- remove_test_records(action_oracle, "ACTION_NO")

# Filter for "Active" records
action <- action %>%
  filter(ACTIVE == "Yes")

# Rename date fields
action <- action %>%
  rename_with(.fn = str_to_lower, 
              .cols = ends_with("_date"))

# Set engagement level integer, risk_cat_code
action <- action %>%
  mutate(eng_level = as.numeric(str_extract(ENG_LEVEL, "\\d")))

# Cleanup action number for sorting
action <- format_id(action, "ACTION_NO")

# Create hyperlink
action <- id_link(action, "action_no")

# Remove unused fields
action <- action %>%
  select(!c(FK_TABLE_ID))

# Reorder fields
action <- action %>%
  relocate(start_date, .after = ACTION) %>%
  relocate(end_date, .after = start_date) %>%
  relocate(poc_review_date, .after = TECHNICAL_POC) %>%
  relocate(eng_level, .after = ENG_LEVEL)

# Remove duplicates and sort
action <- action %>%
  distinct(action_no, .keep_all = TRUE) %>%
  arrange(action_no)

# Cleanup
#rm(action_oracle)
```

```{r wrangle-decision, echo=FALSE, warning=FALSE, message=FALSE}
# Remove test records
decision <- remove_test_records(decision_oracle, "DECISION_NO")

# Filter for "Active" records
decision <- decision %>%
  filter(ACTIVE == "Yes")

# Rename date fields
decision <- decision %>%
  rename_with(.fn = str_to_lower, 
              .cols = ends_with("_date"))

# Set engagement level integer, risk_cat_code
decision <- decision %>%
  mutate(eng_level = as.numeric(str_extract(ENG_LEVEL, "\\d")))

# Cleanup action number for sorting
decision <- format_id(decision, "DECISION_NO")

# Create hyperlink
decision <- id_link(decision, "decision_no")

# Remove unused fields
decision <- decision %>%
  select(!c(FK_TABLE_ID))

# Reorder fields
decision <- decision %>%
  relocate(decision_date, .after = DECISION) %>%
  relocate(poc_review_date, .after = TECHNICAL_POC) %>%
  relocate(eng_level, .after = ENG_LEVEL)

# Remove duplicates and sort
decision <- decision %>%
  distinct(decision_no, .keep_all = TRUE) %>%
  arrange(decision_no)

# Cleanup
#rm(decision_oracle)
```


<!-- Wrangle Related Items -->
```{r wrangle-rel-action-action, echo=FALSE, warning=FALSE, message=FALSE}
# Remove test records
rel_action_action <- remove_test_records(rel_action_action_oracle, "ACTION_NO")
rel_action_action <- remove_test_records(rel_action_action, "RELATED_ACTION")

# Filter for "Active" records
rel_action_action <- rel_action_action %>%
  filter(ACTION_ACTIVE == "Yes" & REL_ACTION_ACTIVE == "Yes")

# Cleanup id numbers for sorting
rel_action_action <- format_id(rel_action_action, "ACTION_NO")
rel_action_action <- format_id(rel_action_action, "RELATED_ACTION")

# Create hyperlink to related item
rel_action_action <- id_link(rel_action_action, "related_action")

# Reorder fields
rel_action_action <- rel_action_action %>%
  relocate(REL_ACTION_ACTIVE, .after = related_action_link)

# Cleanup
#rm(rel_action_action_oracle)
```

```{r wrangle-rel-dec-actionc, echo=FALSE, warning=FALSE, message=FALSE}
# Remove test records
rel_dec_action <- remove_test_records(rel_dec_action_oracle, "DECISION_NO")
rel_dec_action <- remove_test_records(rel_dec_action, "ACTION_NO")

# Filter for "Active" records
rel_dec_action <- rel_dec_action %>%
  filter(DECISION_ACTIVE == "Yes" & ACTION_ACTIVE == "Yes")

# Cleanup id numbers for sorting
rel_dec_action <- format_id(rel_dec_action, "DECISION_NO")
rel_dec_action <- format_id(rel_dec_action, "ACTION_NO")

# Create hyperlinks
rel_dec_action <- id_link(rel_dec_action, "decision_no")
rel_dec_action <- id_link(rel_dec_action, "action_no")

# Reorder fields
rel_dec_action <- rel_dec_action %>%
  relocate(ACTION_ACTIVE, .after = action_no_link)

# Cleanup
#rm(rel_dec_action_oracle)
```

```{r wrangle-rel-dec-dec, echo=FALSE, warning=FALSE, message=FALSE}
# Remove test records
rel_dec_dec <- remove_test_records(rel_dec_dec_oracle, "DECISION_NO")
rel_dec_dec <- remove_test_records(rel_dec_dec, "RELATED_DECISION")

# Filter for "Active" records
rel_dec_dec <- rel_dec_dec %>%
  filter(DECISION_ACTIVE == "Yes" & REL_DEC_ACTIVE == "Yes")

# Cleanup id numbers for sorting
rel_dec_dec <- format_id(rel_dec_dec, "DECISION_NO")
rel_dec_dec <- format_id(rel_dec_dec, "RELATED_DECISION")

# Create hyperlink to related item
rel_dec_dec <- id_link(rel_dec_dec, "related_decision")

# Reorder fields
rel_dec_dec <- rel_dec_dec %>%
  relocate(REL_DEC_ACTIVE, .after = related_decision_link)

# Cleanup
#rm(rel_dec_dec_oracle)
```

```{r wrangle-rel-risk-action, echo=FALSE, warning=FALSE, message=FALSE}
# Remove test records
rel_risk_action <- remove_test_records(rel_risk_action_oracle, "RISK_NO")
rel_risk_action <- remove_test_records(rel_risk_action, "ACTION_NO")

# Filter for "Active" records
rel_risk_action <- rel_risk_action %>%
  filter(RISK_ACTIVE == "Yes" & ACTION_ACTIVE == "Yes")

# Cleanup id fields for sorting
rel_risk_action <- format_id(rel_risk_action, "RISK_NO")
rel_risk_action <- format_id(rel_risk_action, "ACTION_NO")

# Create hyperlink
rel_risk_action <- id_link(rel_risk_action, "risk_no")
rel_risk_action <- id_link(rel_risk_action, "action_no")

# Reorder fields
rel_risk_action <- rel_risk_action %>%
  relocate(ACTION_ACTIVE, .after = action_no_link)

# Cleanup
#rm(rel_risk_action_oracle)
```

```{r wrangle-rel-risk-dec, echo=FALSE, warning=FALSE, message=FALSE}
# Remove test records
rel_risk_dec <- remove_test_records(rel_risk_dec_oracle, "RISK_NO")
rel_risk_dec <- remove_test_records(rel_risk_dec, "DECISION_NO")

# Filter for "Active" records
rel_risk_dec <- rel_risk_dec %>%
  filter(RISK_ACTIVE == "Yes" & DECISION_ACTIVE == "Yes")

# Cleanup id fields for sorting
rel_risk_dec <- format_id(rel_risk_dec, "RISK_NO")
rel_risk_dec <- format_id(rel_risk_dec, "DECISION_NO")

# Create hyperlink
rel_risk_dec <- id_link(rel_risk_dec, "risk_no")
rel_risk_dec <- id_link(rel_risk_dec, "decision_no")

# Reorder fields
rel_risk_dec <- rel_risk_dec %>%
  relocate(DECISION_ACTIVE, .after = decision_no_link)

# Cleanup
#rm(rel_risk_dec_oracle)
```

```{r wrangle-rel-risk-risk, echo=FALSE, warning=FALSE, message=FALSE}
# Remove test records
rel_risk_risk <- remove_test_records(rel_risk_risk_oracle, "RISK_NO")
rel_risk_risk <- remove_test_records(rel_risk_risk, "RELATED_RISK")

# Filter for "Active" records
rel_risk_risk <- rel_risk_risk %>%
  filter(RISK_ACTIVE == "Yes" & REL_RISK_ACTIVE == "Yes")

# Cleanup id numbers for sorting
rel_risk_risk <- format_id(rel_risk_risk, "RISK_NO")
rel_risk_risk <- format_id(rel_risk_risk, "RELATED_RISK")

# Create hyperlink to Related Risk
rel_risk_risk <- id_link(rel_risk_risk, "related_risk")

# Reorder fields
rel_risk_risk <- rel_risk_risk %>%
  relocate(REL_RISK_ACTIVE, .after = related_risk_link)

# Cleanup
#rm(rel_risk_risk_oracle)
```

<!-- Create Timelines -->
```{r create_timevis_df, echo=FALSE, warning=FALSE, message=FALSE}
# Create a timevis "data" data frame of risks
risk_time <- risk %>%
  arrange(risk_no) %>%
  select(OBJECTID, risk_no, start_date, end_date, risk_cat_code, 
         CONCERNS, FEATURE, TECHNICAL_POC, eng_level) %>%
  rename(id = OBJECTID) %>%
  rename(content = risk_no) %>%
  relocate(id, .before = content) %>%
  rename(start = start_date) %>%
  rename(end = end_date) %>%
  rename(title = CONCERNS) %>%
  relocate(title, .after = content) %>%
  mutate(group = as.numeric(factor(risk_cat_code))) %>%
  relocate(group, .after = end)

# Create a timevis "group" data frame to group risks by unique Risk Categories
risk_time_riskcategory <- risk %>%
  select(risk_cat_code, RISKCATEGORY) %>%
  mutate(id = as.numeric(factor(risk_cat_code))) %>%
  rename(content = risk_cat_code) %>%
  rename(title = RISKCATEGORY) %>%
  relocate(id, .before = content) %>%
  distinct(id, content, .keep_all = TRUE)
```

```{r create-items, echo=FALSE, warning=FALSE, message=FALSE}
# Create a df of all items (risks, actions, decisions)
risk_items <- risk %>%
  select(risk_no, risk_no_link, CONCERNS, id_type, 
         FEATURE, DISCIPLINE) %>%
  rename(item_id = risk_no,
         item_link = risk_no_link,
         description = CONCERNS)

action_items <- action %>%
  select(action_no, action_no_link, ACTION, id_type, 
         FEATURE, DISCIPLINE) %>%
  rename(item_id = action_no,
         item_link = action_no_link,
         description = ACTION)

decision_items <- decision %>%
  select(decision_no, decision_no_link, DECISION, id_type, 
         FEATURE, DISCIPLINE) %>%
  rename(item_id = decision_no,
         item_link = decision_no_link,
         description = DECISION)

items <- bind_rows(risk_items, action_items, decision_items)
rm(risk_items, action_items, decision_items)
```

```{r create-relations, echo=FALSE, warning=FALSE, message=FALSE}
# Create a df of all relationships
rel_a_a <- rel_action_action %>%
  select(action_no, related_action) %>%
  rename(from = action_no,
         to = related_action) %>%
  mutate(id_type_1 = "action",
         id_type_2 = "action")
  
rel_d_a <- rel_dec_action %>%
  select(decision_no, action_no) %>%
  rename(from = decision_no,
         to = action_no) %>%
  mutate(id_type_1 = "decision",
         id_type_2 = "action")

rel_d_d <- rel_dec_dec %>%
  select(decision_no, related_decision) %>%
  rename(from = decision_no,
         to = related_decision) %>%
  mutate(id_type_1 = "decision",
         id_type_2 = "decision")

rel_r_a <- rel_risk_action %>%
  select(risk_no, action_no) %>%
  rename(from = risk_no,
         to = action_no) %>%
  mutate(id_type_1 = "risk",
         id_type_2 = "action")

rel_r_d <- rel_risk_dec %>%
  select(risk_no, decision_no) %>%
  rename(from = risk_no,
         to = decision_no) %>%
  mutate(id_type_1 = "risk",
         id_type_2 = "decision")

rel_r_r <- rel_risk_risk %>%
  select(risk_no, related_risk) %>%
  rename(from = risk_no,
         to = related_risk) %>%
  mutate(id_type_1 = "risk",
         id_type_2 = "risk")

relations <- bind_rows(rel_a_a, rel_d_a, rel_d_d, rel_r_a, rel_r_d, rel_r_r) %>%
  drop_na()

# Cleanup
rm(rel_a_a, rel_d_a, rel_d_d, rel_r_a, rel_r_d, rel_r_r)
```

```{r network-analysis, echo=FALSE, warning=FALSE, message=FALSE}
# Create the igraph object for network analysis
relate_igraph <- igraph::graph_from_data_frame(d = relations, 
                                               vertices = items, 
                                               directed = FALSE)

# Set vertex colors and size
clr <- as.factor(V(relate_igraph)$id_type)
levels(clr) <- c("#D55E00", "#E69F00", "#0072B2")
igraph::V(relate_igraph)$color <- as.character(clr)
igraph::V(relate_igraph)$size  <- igraph::degree(relate_igraph)*5

# Identify blocks of related items
relate_igraph_simp <- igraph::simplify(relate_igraph, 
                                       remove.multiple = TRUE,
                                       remove.loops = TRUE)
itemBlocks <- igraph::cohesive_blocks(relate_igraph_simp)

# Extract of items within each block
blocks_df <- as.data.frame(t(sapply(itemBlocks$blocks, as_ids)))

block_list <- list()

for(i in 2:length(colnames(blocks_df))) {
  block_item <- data.frame(block_no = paste("Block", i - 1),
                           item_id = unlist(blocks_df[[i]]))
  block_list[[i]] <- block_item
}

blocks <- bind_rows(block_list)

# Calculate count of related items for each item
adjacent_items <- igraph::as_adj_list(relate_igraph_simp)
adj_df <- as.data.frame(t(sapply(adjacent_items, as_ids)))

adj_list <- list()

for(i in 1:length(colnames(adj_df))) {
  if(length(adj_df[[i]][[1]]) > 0) { 
    adj_item <- data.frame(item_id = colnames(adj_df)[[i]],
                           rel_item_id = adj_df[[i]][[1]])
    adj_list[[i]] <- adj_item
  }
}

adj_items <- bind_rows(adj_list)

adj_count <- adj_items %>%
  group_by(item_id) %>%
  summarise(adj_count = n())

# Calculate item centrality - degree
item_degree <- stack(igraph::degree(relate_igraph))
item_degree <- item_degree %>%
  mutate(item_id = as.character(ind)) %>%
  rename(degree = values) %>%
  relocate(item_id, .before = degree) %>%
  select(c(!ind))

# Join blocks to items to add key attributes
related_blocks <- blocks %>%
  left_join(item_degree, by = c("item_id" = "item_id")) %>%
  left_join(adj_count, by = c("item_id" = "item_id")) %>%
  left_join(items, by = c("item_id" = "item_id")) %>%
  arrange(block_no, desc(degree))

rm(blocks_df, block_list, blocks, adjacent_items, adj_df, adj_list, adj_items, 
   adj_count, item_degree)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Create dendrogram
eb <- cluster_edge_betweenness(relate_igraph)
#plot_dendrogram(eb)
```

