--- 
title: "Brandon Road Interbasin Project Risk Analysis Report"
author: "USACE Rock Island District"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
description: "Report description goes here."
bibliography: [book.bib, packages.bib]
biblio-style: apalike
csl: chicago-fullnote-bibliography.csl
---

# Introduction {-}

## Project 
* P2 project name: Brandon Rd-Great Lakes/Miss Rvr Interbasin
* P2 project number: 482782
* P2 program code: 451617

## Architecture
This report using the following architecture:  

* **Data Entry** - An [Oracle APEX](https://apex.oracle.com/) web-database application stores the risk analysis data and allows project risk managers to enter and edit the data. This application resides on the USACE intranet (CorpsNet) and is only available for editing to project risk managers.  
* **Reporting** - This report is produced using [R]()  
* **Code Repository** -   
* **Static Website Publishing** -   
* **Project Viewer** -   

```{r, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.cap="Report Architecture"}
knitr::include_graphics(path = "diagrams/cloud_arch-workflow.drawio.svg")
```

<!-- Libraries -->
```{r library, include=FALSE}
library(tidyverse)
library(knitr)
library(rmarkdown)
library(rlang)
library(lubridate)
library(DBI)
library(ROracle)
library(keyring)
library(tools)
library(kableExtra)
library(pander)
library(timevis)
library(treemapify)
library(gridExtra)
library(formattable)
library(igraph)
library(edgebundleR)
library(downloadthis)
library(rarr)
```

```{r source, include=FALSE}
#source("R/risk_register_table.R")
#source("R/decision_register_table.R")
#source("R/action_register_table.R")
#source("R/atx_header.R")
#source("R/pandoc_header.R")
#source("R/percent_treemap.R")
#source("R/timeline.R")
#source("R/format_id.R")
#source("R/id_link.R")
#source("R/eng_level_history.R")
#source("R/discussion_table.R")
#source("R/related_block_table.R")
#source("R/remove_test_records.R")
#source("R/impact_outcome_table.R")
#source("R/risk_pies.R")
```


<!-- Report Constants -->
```{r, include=FALSE}
qa_email_address <- "Casey.I.Lewis@usace.army.mil"
current_date <- lubridate::today()
```

```{r, include=FALSE}
# Use the `keyring` package to save the database username and password in the 
# system credential store
key_service <- "egis-db-brandonroad"
user_name <- "BrandonRoad"
# Set once on each computer prior to building book
#keyring::key_set(service = key_service, username = user_name)

# Make Oracle connection
drv  <- DBI::dbDriver("Oracle")
host <- "egis-db"
port <- "1521"
sid  <- "B5SDEDP1"
connect_string <- paste0(
  "(DESCRIPTION=",
  "(ADDRESS=(PROTOCOL=tcp)(HOST=", host, ")(PORT=", port, "))",
  "(CONNECT_DATA=(SID=", sid, ")))")
 
con_roracle <- ROracle::dbConnect(drv, 
                                  username = user_name, 
                                  password = keyring::key_get(key_service,
                                                              user_name),
                                  dbname   = connect_string)
```


```{r, include=FALSE}
# Import tables from Oracle
risk_oracle              <- ROracle::dbReadTable(con_roracle, 
                                                 "RISK_MAIN_VIEW")
events_oracle            <- ROracle::dbReadTable(con_roracle, 
                                                 "EVENTS_MAIN_VIEW")
discussion_oracle        <- ROracle::dbReadTable(con_roracle, 
                                                 "DISCUSSION_LOG_MAIN_VIEW")
action_oracle            <- ROracle::dbReadTable(con_roracle, 
                                                 "ACTION_MAIN_VIEW")
decision_oracle          <- ROracle::dbReadTable(con_roracle, 
                                                 "DECISION_MAIN_VIEW")
rel_action_action_oracle <- ROracle::dbReadTable(con_roracle, 
                                                 "REL_ACTION_ACTION_MAIN_VIEW")
rel_dec_dec_oracle       <- ROracle::dbReadTable(con_roracle, 
                                                 "REL_DEC_DEC_MAIN_VIEW")
rel_dec_action_oracle    <- ROracle::dbReadTable(con_roracle, 
                                                 "REL_DEC_ACTION_MAIN_VIEW")
rel_risk_action_oracle   <- ROracle::dbReadTable(con_roracle, 
                                                 "REL_RISK_ACTION_MAIN_VIEW")
rel_risk_dec_oracle      <- ROracle::dbReadTable(con_roracle, 
                                                 "REL_RISK_DEC_MAIN_VIEW")
rel_risk_risk_oracle     <- ROracle::dbReadTable(con_roracle, 
                                                 "REL_RISK_RISK_MAIN_VIEW")

# Disconnect from the database
ROracle::dbDisconnect(con_roracle)
```


<!-- Wrangle Risk/Action/Decision Data -->
```{r wrangle-risk, include=FALSE}
risk<-rarr::wrangle_risk(risk_oracle)
```

```{r write-risk, include=FALSE}
risk %>%
  select(!c(OBJECTID, risk_no_link)) %>%
  write_csv(file = "download/risk.csv", quote = "all")
```


```{r wrangle-events, include=FALSE}
events<-rarr::wrangle_events(events_oracle)
```

```{r wrangle-discussion, include=FALSE}
discussion<-rarr::wrangle_discussion(discussion_oracle)

```

```{r wrangle-action, include=FALSE}
action<-rarr::wrangle_action(action_oracle)

```

```{r wrangle-decision, include=FALSE}
decision<-rarr::wrangle_decision(decision_oracle)

```


<!-- Wrangle Related Items -->
```{r wrangle-rel-action-action, include=FALSE}
rel_action_action<-rarr::wrangle_rel_action_action(rel_action_action_oracle)

```

```{r wrangle-rel-dec-action, include=FALSE}
rel_dec_action <- rarr::wrangle_rel_dec_action(rel_dec_action_oracle)

```

```{r wrangle-rel-dec-dec, include=FALSE}
rel_dec_dec<- rarr::wrangle_rel_dec_dec(rel_dec_dec_oracle)

```

```{r wrangle-rel-risk-action, include=FALSE}
rel_risk_action<-rarr::wrangle_rel_risk_action(rel_risk_action_oracle)

```

```{r wrangle-rel-risk-dec, include=FALSE}
rel_risk_dec<- rarr::wrangle_rel_risk_dec(rel_risk_dec_oracle)

```

```{r wrangle-rel-risk-risk, include=FALSE}
rel_risk_risk<-rarr::wrangle_rel_risk_risk(rel_risk_risk_oracle)

```

<!-- Create Timelines -->
```{r create_timevis_df, include=FALSE}
# Create a timevis "data" data frame of risks
risk_time <- rarr::wrangle_risk_time(risk)

# Create a timevis "group" data frame to group risks by unique Risk Categories
risk_time_riskcategory <- rarr::wrangle_risk_time_riskcat(risk) 

```

```{r create-items, include=FALSE}
# Create a df of all items (risks, actions, decisions)
items <- rarr::create_items(risk, action, decision)

```

```{r create-relations, include=FALSE}
# Create a df of all relationships
relations<-rarr::create_relations(rel_action_action, rel_dec_action, rel_dec_dec,                          rel_risk_action,rel_risk_dec,rel_risk_risk)

```

```{r network-analysis, include=FALSE}
# Create the igraph object for network analysis
relate_igraph <- igraph::graph_from_data_frame(d = relations, 
                                               vertices = items, 
                                               directed = FALSE)

related_blocks<-rarr::network_analysis(relate_igraph, items)

```

```{r dendrogram, include=FALSE}
# Create dendrogram
eb <- cluster_edge_betweenness(relate_igraph)
#plot_dendrogram(eb)
```

