<!-- Wrangle report data -->
```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Set iterator variable for testing. Comment out in production. 
# x <- "ACT-001"

# Filter the decisions df for the current decision item
action_item <- action %>%
  filter(action_no == x)

# Filter events df for the current decision item
events_item <- events %>%
  filter(TABLE_NAME == "ACTION_REGISTER") %>%
  filter(fk_table_id == x)

# Filter discussion df for the current decision item
discussion_item <- discussion %>%
  filter(TABLE_NAME == "ACTION_REGISTER") %>%
  filter(fk_table_id == x)

# Filter related decisions df for the current decision item
rel_action_action_item <- rel_action_action %>%
  filter(action_no == x)

# Filter related actions df for the current decision item
rel_dec_action_item <- rel_dec_action %>%
  filter(action_no == x)

# Filter related risks df for the current decision item
rel_risk_action_item <- rel_risk_action %>%
  filter(action_no == x)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
action_feedback_link <- paste0("mailto:", 
                               qa_email_address, 
                               "?subject=Action Item: ", 
                               action_item$action_no,
                               "&body=Please describe the changes you would recommend for this action item: %0D%0A
                                 %0D%0A")
```

<!-- Action Item -->
:::::::::::::: {.item-box}

::: {.right}
[&circlearrowright;](`r action_feedback_link`)
:::

::: {.header}
```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
rarr::pandoc_header(text = action_item$action_no, 
              level = action_heading_level,
              identifier = paste0(action_identifier_prefix, "-",
                                  str_to_lower(action_item$action_no)),
              number = FALSE,
              list = list_action_item)
```
:::

`r action_item$ACTION`

:::::::: {.section-box}
<!-- Risk Attributes line 1 -->
::::: {.grid-5w-2h}
::: {.var-name}
Start Date
:::
::: {.var-value}
`r action_item$start_date`
:::
::: {.var-name}
End Date
:::
::: {.var-value}
`r action_item$end_date`
:::
::: {.var-name}
Engagement Level
:::
::: {.var-value}
`r action_item$ENG_LEVEL`
:::
::: {.var-name}
Feature
:::
::: {.var-value}
`r action_item$FEATURE`
:::
::: {.var-name}
Discipline
:::
::: {.var-value}
`r action_item$DISCIPLINE`
:::
:::::

<!-- Risk Attributes line 2 -->
::::: {.grid-5w-2h}
::: {.var-name}
Owner
:::
::: {.var-value}
`r action_item$OWNER`
:::
::: {.var-name}
Technical POC
:::
::: {.var-value}
`r action_item$TECHNICAL_POC`
:::
::: {.var-name}
Last Review Date
:::
::: {.var-value}
`r action_item$poc_review_date`
:::
:::::
::::::::

:::::: {.white-box}
`r cat(' ')`
::::::

:::::::: {.section-box}
**Engagement Level History**
```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
if(length(events_item$FK_TABLE_ID) > 0) {
  rarr::eng_level_history(events_item, events_item$fk_table_id, 
                    show_item_link = FALSE)
} else {
  cat("Engagement Level not set.")
}
```

<!-- End Risk Engagement Level History -->
::::::::  

:::::: {.white-box}
`r cat(' ')`
::::::

:::::::: {.section-box}  
**Discussion Items**
```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
if(length(discussion_item$fk_table_id) > 0) {
  rarr::discussion_table(discussion_item, discussion_item$fk_table_id)
} else {
  cat(" No discussion items.")
}
```

<!-- End Risk Discussion Items -->
:::::::: 

::::::::: {.section-box}
**Related Actions**
```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
if(length(rel_action_action_item$related_decision) > 0) {
  kbl(select(rel_action_action_item, related_action_link, RELATED_ACTION),
      col.names = c("Number", "Description")) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", 
                                        "responsive"),
                  full_width = TRUE, 
                  position = "left") %>%
    column_spec(1, width = "10em")
} else {
  cat(" No related decisions.")
}
```

:::::::::  

:::::: {.white-box}
`r cat(' ')`
::::::

:::::::::::: {.section-box}
**Response Plan**

::::::::: {.section-box}
**Related Decisions**
```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
if(length(rel_dec_action_item$decision_no) > 0) {
  kbl(select(rel_dec_action_item, decision_no_link, DECISION),
      col.names = c("Number", "Description")) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", 
                                        "responsive"),
                  full_width = TRUE, 
                  position = "left") %>%
    column_spec(1, width = "10em")
} else {
  cat(" No related decisions.")
}
```

:::::::::

:::::: {.white-box}
`r cat(' ')`
::::::

::::::::: {.section-box}
**Related Risks**
```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
if(length(rel_risk_action_item$risk_no) > 0) {
  kbl(select(rel_risk_action_item, risk_no_link, CONCERNS),
      col.names = c("Number", "Description")) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", 
                                        "responsive"),
                  full_width = TRUE, 
                  position = "left") %>%
    column_spec(1, width = "10em")
} else {
  cat(" No related risks.")
}
```

:::::::::

<!-- End Response Plan -->
::::::::::::  


<!-- End Action Item -->
:::::::::::::: 

:::::: {.white-box}
`r cat(' ')`
::::::
