<!-- Wrangle report data -->
```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Set iterator variable for testing. Comment out in production. 
# x <- "DEC-001"

# Filter the decisions df for the current decision item
decision_item <- decision %>%
  filter(decision_no == x)

# Filter events df for the current decision item
events_item <- events %>%
  filter(TABLE_NAME == "DECISION_REGISTER") %>%
  filter(fk_table_id == x)

# Filter discussion df for the current decision item
discussion_item <- discussion %>%
  filter(TABLE_NAME == "DECISION_REGISTER") %>%
  filter(fk_table_id == x)

# Filter related decisions df for the current decision item
rel_dec_dec_item <- rel_dec_dec %>%
  filter(decision_no == x)

# Filter related actions df for the current decision item
rel_dec_action_item <- rel_dec_action %>%
  filter(decision_no == x)

# Filter related risks df for the current decision item
rel_risk_dec_item <- rel_risk_dec %>%
  filter(decision_no == x)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
decision_feedback_link <- paste0("mailto:", 
                                 qa_email_address, 
                                 "?subject=Decision Item: ", 
                                 decision_item$decision_no,
                                 "&body=Please describe the changes you would recommend for this decision item: %0D%0A
                                 %0D%0A")
```

<!-- Decision Item -->
:::::::::::::: {.item-box}

::: {.right}
[&circlearrowright;](`r decision_feedback_link`)
:::

::: {.header}
```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
pandoc_header(text = decision_item$decision_no, 
              level = decision_heading_level,
              identifier = paste0(decision_identifier_prefix, "-",
                                  str_to_lower(decision_item$decision_no)),
              number = FALSE,
              list = list_decision_item)
```
:::

`r decision_item$DECISION`

:::::::: {.section-box}
<!-- Risk Attributes line 1 -->
::::: {.grid-5w-2h}
::: {.var-name}
Approval Status
:::
::: {.var-value}
`r decision_item$APPROVAL_STATUS`
:::
::: {.var-name}
Decision Date
:::
::: {.var-value}
`r decision_item$decision_date`
:::
::: {.var-name}
Engagement Level
:::
::: {.var-value}
`r decision_item$ENG_LEVEL`
:::
::: {.var-name}
Feature
:::
::: {.var-value}
`r decision_item$FEATURE`
:::
::: {.var-name}
Discipline
:::
::: {.var-value}
`r decision_item$DISCIPLINE`
:::
:::::

<!-- Risk Attributes line 2 -->
::::: {.grid-5w-2h}
::: {.var-name}
Technical POC
:::
::: {.var-value}
`r decision_item$TECHNICAL_POC`
:::
::: {.var-name}
Last Review Date
:::
::: {.var-value}
`r decision_item$poc_review_date`
:::
:::::

<!-- Risk Attributes line 3 -->
::::: {.grid-5w-2h}
::: {.var-name}
Rationale
:::
::: {.var-value}
`r decision_item$RATIONALE`
:::
:::::

<!-- Risk Attributes line 4 -->
::::: {.grid-5w-2h}
::: {.var-name}
Implications
:::
::: {.var-value}
`r decision_item$IMPLICATIONS`
:::
:::::

<!-- Risk Attributes line 5 -->
::::: {.grid-5w-2h}
::: {.var-name}
Outcomes
:::
::: {.var-value}
`r decision_item$OUTCOMES`
:::
:::::
::::::::

:::::: {.white-box}
`r cat(' ')`
::::::

:::::::: {.section-box}
**Engagement Level History**
```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
if(length(events_item$FK_TABLE_ID) > 0) {
  kbl(select(events_item, ENG_LEVEL, level_date, DESCRIPTION, duration_days),
      col.names = c("Level", "Date", "Reason for level change", 
                    "Duration (days)")) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", 
                                      "responsive"),
                  full_width = TRUE, 
                  position = "left") %>%
    column_spec(1, width = "6em") %>%
    column_spec(2, width = "8em")
} else {
  cat("Engagement Level not set.")
}
```

<!-- End Risk Engagement Level History -->
::::::::  

:::::: {.white-box}
`r cat(' ')`
::::::

:::::::: {.section-box}  
**Discussion Items**
```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
if(length(discussion_item$fk_table_id) > 0) {
kbl(select(discussion_item, DISCUSSION, RESPONSIBLE_POC, poc_review_date),
    col.names = c("Discussion Topic", "POC", "Date")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", 
                                      "responsive")) 
} else {
  cat(" No discussion items.")
}
```

<!-- End Risk Discussion Items -->
:::::::: 

:::::: {.white-box}
`r cat(' ')`
::::::

::::::::: {.section-box}
**Related Decisions**

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
if(length(rel_dec_dec_item$related_decision_no) > 0) {
  kbl(select(rel_dec_dec_item, related_decision_link, RELATED_DECISION),
      col.names = c("Number", "Description")) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", 
                                        "responsive"),
                  full_width = TRUE, 
                  position = "left") %>%
    column_spec(1, width = "10em")
} else {
  cat(" No related decisions.")
}
```

:::::::::  

:::::: {.white-box}
`r cat(' ')`
::::::

:::::::::::: {.section-box}
**Response Plan**

::::::::: {.section-box}
**Related Actions**
```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
if(length(rel_dec_action_item$action_no) > 0) {
  kbl(select(rel_dec_action_item, action_no_link, ACTION),
      col.names = c("Number", "Description")) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", 
                                        "responsive"),
                  full_width = TRUE, 
                  position = "left") %>%
    column_spec(1, width = "10em")
} else {
  cat(" No related actions.")
}
```

:::::::::

:::::: {.white-box}
`r cat(' ')`
::::::

::::::::: {.section-box}
**Related Risks**
```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
if(length(rel_risk_dec_item$risk_no) > 0) {
  kbl(select(rel_risk_dec_item, risk_no_link, CONCERNS),
      col.names = c("Number", "Description")) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", 
                                        "responsive"),
                  full_width = TRUE, 
                  position = "left") %>%
    column_spec(1, width = "10em")
} else {
  cat(" No related risks.")
}
```

:::::::::

<!-- End Response Plan -->
::::::::::::  


<!-- End Decision Item -->
:::::::::::::: 

:::::: {.white-box}
`r cat(' ')`
::::::
