```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
# Subset for the current risk item
risk_item <- risk %>%
  dplyr::filter(risk_no == x)
```


```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
pander::pandoc.header(risk_item$risk_no, level = 2)
pander::pandoc.p(risk_item$CONCERNS)
```

::::: {.grid-5w-2h}
::: {.var-name}
Start Date
:::
::: {.var-value}
`r risk_item$start_date`
:::
::: {.var-name}
End Date
:::
::: {.var-value}
`r risk_item$end_date`
:::
::: {.var-name}
Risk Category
:::
::: {.var-value}
`r risk_item$RISKCATEGORY`
:::
::: {.var-name}
Engagement Level
:::
::: {.var-value}
`r risk_item$ENG_LEVEL`
:::
::::: 


::::: {.grid-5w-2h}
::: {.var-name}
Risk Strategy
:::
::: {.var-value}
`r risk_item$RISK_STRATEGY`
:::
::: {.var-name}
Component
:::
::: {.var-value}
`r risk_item$COMPONENT`
:::
::: {.var-name}
Discipline
:::
::: {.var-value}
`r risk_item$DISCIPLINE`
:::
::: {.var-name}
Risk Opportunity Event
:::
::: {.var-value}
`r risk_item$RISK_OPPORTUNITY_EVENT`
:::
::: {.var-name}
Timing of Delay
:::
::: {.var-value}
`r risk_item$TIMING_OF_DELAY`
:::
:::::


::::: {.grid-5w-2h}
::: {.var-name}
POC
:::
::: {.var-value}
`r risk_item$RESPONSIBLE_POC`
:::
::: {.var-name}
Last Review Date
:::
::: {.var-value}
`r risk_item$POC_REVIEW_DATE`
:::
:::::



```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
pander::pandoc.p('')
```
