<!-- Wrangle report data -->
```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Set iterator variable for testing. Comment out in production. 
#x <- "TR-023"

# Filter the risks df for the current risk item
risk_item <- risk %>%
  filter(risk_no == x)

# Filter events df for the current risk item
events_item <- events %>%
  filter(TABLE_NAME == "RISK_REGISTER") %>%
  filter(fk_table_id == x)

# Filter discussion df for the current risk item
discussion_item <- discussion %>%
  filter(TABLE_NAME == "RISK_REGISTER") %>%
  filter(fk_table_id == x)

# Filter related risks df for the current risk item
rel_risk_risk_item <- rel_risk_risk %>%
  filter(risk_no == x)

# Filter related actions df for the current risk item
rel_risk_action_item <- rel_risk_action %>%
  filter(risk_no == x)

# Filter related decisions df for the current risk item
rel_risk_dec_item <- rel_risk_dec %>%
  filter(risk_no == x)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Transpose cost fields to long format
cost_risk <- risk_item %>%
  select(COST_LIKELIHOOD, COST_IMPACT, COST_IMPACT_PER_PROJECT, 
         COST_RISK, cost_risk_color) %>%
  pivot_longer(cols = starts_with(c("COST", "cost")), 
               names_to = "cost_variable", 
               values_to = "cost") %>%
  mutate(variable = substring(cost_variable, 6, 23)) %>%
  mutate(variable = str_replace_all(variable, "_", " ")) %>%
  mutate(variable = str_to_lower(variable)) %>%
  mutate(variable = str_to_title(variable))

# Transpose schedule fields to long format
schedule_risk <- risk_item %>%
  select(SCHEDULE_LIKELIHOOD, SCHEDULE_IMPACT, SCHEDULE_IMPACT_PER_PROJECT, 
         SCHEDULE_RISK, schedule_risk_color) %>%
  pivot_longer(cols = starts_with(c("SCHEDULE", "schedule")), 
               names_to = "schedule_variable", 
               values_to = "schedule") %>%
  mutate(variable = substring(schedule_variable, 10, 27)) %>%
  mutate(variable = str_replace_all(variable, "_", " ")) %>%
  mutate(variable = str_to_lower(variable)) %>%
  mutate(variable = str_to_title(variable))

# Transpose efficacy fields to long format
efficacy_risk <- risk_item %>%
  select(EFFICACY_LIKELIHOOD, EFFICACY_IMPACT, EFFICACY_IMPACT_PER_PROJECT, 
         EFFICACY_RISK, efficacy_risk_color) %>%
  pivot_longer(cols = starts_with(c("EFFICACY", "efficacy")), 
               names_to = "efficacy_variable", 
               values_to = "efficacy") %>%
  mutate(variable = substring(efficacy_variable, 10, 27)) %>%
  mutate(variable = str_replace_all(variable, "_", " ")) %>%
  mutate(variable = str_to_lower(variable)) %>%
  mutate(variable = str_to_title(variable))

# Combine cost and schedule values into a single table
cost_schedule_risk <- cost_risk %>%
  select(variable, cost) %>%
  inner_join(select(schedule_risk, variable, schedule), 
             by = "variable")

risk_rating <- efficacy_risk %>%
  select(variable, efficacy) %>%
  inner_join(select(cost_schedule_risk, variable, cost, schedule),
             by = "variable")

# Replace any NA values with ""
risk_rating[is.na(risk_rating)] <- ""
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
feedback_link <- paste0("mailto:", qa_email_address, 
                        "?subject=Risk Item: ", risk_item$risk_no,
                        "&body=Please describe the changes you would recommend for this risk item: %0D%0A
                         %0D%0A")
```

<!-- Format report -->
:::::::::::::: {.item-box}

::: {.right}
[&circlearrowright;](`r feedback_link`)
:::

::: {.header}
```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
pandoc_header(text = risk_item$risk_no, 
              level = risk_heading_level,
              identifier = paste0(risk_identifier_prefix, "-",
                                  str_to_lower(risk_item$risk_no)),
              number = FALSE,
              list = list_risk_item)
```
:::

`r risk_item$CONCERNS`

:::::::: {.section-box}
<!-- Risk Attributes line 1 -->
::::: {.grid-5w-2h}
::: {.var-name}
Risk Category
:::
::: {.var-value}
`r risk_item$RISKCATEGORY`
:::
::: {.var-name}
Engagement Level
:::
::: {.var-value}
`r risk_item$ENG_LEVEL`
:::
::: {.var-name}
Start Date
:::
::: {.var-value}
`r risk_item$start_date`
:::
::: {.var-name}
End Date
:::
::: {.var-value}
`r risk_item$end_date`
:::
::: {.var-name}
Status
:::
::: {.var-value}
`r risk_item$MANAGEMENT_STATUS`
:::
::::: 

<!-- Risk Attributes line 2-->
::::: {.grid-5w-2h}
::: {.var-name}
Risk Strategy
:::
::: {.var-value}
`r risk_item$RISK_STRATEGY`
:::
::: {.var-name}
Feature
:::
::: {.var-value}
`r risk_item$FEATURE`
:::
::: {.var-name}
Discipline
:::
::: {.var-value}
`r risk_item$DISCIPLINE`
:::
::: {.var-name}
Risk Opportunity Event
:::
::: {.var-value}
`r risk_item$RISK_OPPORTUNITY_EVENT`
:::
::: {.var-name}
Timing of Delay
:::
::: {.var-value}
`r risk_item$TIMING_OF_DELAY`
:::
:::::

<!-- Risk Attributes line 3 -->
::::: {.grid-5w-2h}
::: {.var-name}
Owner
:::
::: {.var-value}
`r risk_item$OWNER`
:::
::: {.var-name}
Tech. POC
:::
::: {.var-value}
`r risk_item$TECHNICAL_POC`
:::
::: {.var-name}
Last Review Date
:::
::: {.var-value}
`r risk_item$poc_review_date`
:::
::: {.var-name}
Trend
:::
::: {.var-value}
`r risk_item$TREND`
:::
:::::

<!-- End Risk Attributes -->
::::::::  

:::::: {.white-box}
`r cat(' ')`
::::::

:::::::: {.section-box}
**Efficacy-Cost-Schedule Rating**  
```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
kbl(filter(risk_rating, variable != "Risk Color"),
    col.names = c("", "Efficacy", "Cost", "Schedule")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", 
                                      "responsive"),
                full_width = FALSE, 
                position = "left") %>%
  row_spec(0, bold = TRUE) %>%
  column_spec(1, bold = TRUE, width = "12em", border_right = TRUE) %>%
  column_spec(2, color = "black",
              width = "8em",
              background = ifelse(risk_rating$efficacy == "Low", "green",
                           ifelse(risk_rating$efficacy == "Moderate", "orange",
                           ifelse(risk_rating$efficacy == "High", "red",
                                  "#ffffff00")))) %>%
  column_spec(3, color = "black",
              width = "8em",
              background = ifelse(risk_rating$cost == "Low", "green",
                           ifelse(risk_rating$cost == "Moderate", "orange",
                           ifelse(risk_rating$cost == "High", "red",
                                  "#ffffff00")))) %>%
  column_spec(4, color = "black",
              width = "8em",
              background = ifelse(risk_rating$schedule == "Low", "green",
                           ifelse(risk_rating$schedule == "Moderate", "orange",
                           ifelse(risk_rating$schedule == "High", "red",
                           "#ffffff00"))))
```

<!-- End Cost-Schedule Risk -->
:::::::: 

:::::: {.white-box}
`r cat(' ')`
::::::

:::::::: {.section-box}
**Engagement Level History**
```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
if(length(events_item$FK_TABLE_ID) > 0) {
  kbl(select(events_item, ENG_LEVEL, level_date, DESCRIPTION, duration_days),
      col.names = c("Level", "Date", "Reason for level change", "Duration (days)")) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", 
                                      "responsive"),
                  full_width = TRUE, 
                  position = "left") %>%
    column_spec(1, width = "6em") %>%
    column_spec(2, width = "8em")
} else {
  cat("Engagement Level not set.")
}
```

<!-- End Risk Engagement Level History -->
::::::::  

:::::: {.white-box}
`r cat(' ')`
::::::

:::::::: {.section-box}  
**Discussion Items**
```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
kbl(select(discussion_item, DISCUSSION, RESPONSIBLE_POC, poc_review_date),
    col.names = c("Discussion Topic", "POC", "Date")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", 
                                      "responsive")) 
```

<!-- End Risk Discussion Items -->
:::::::: 

:::::: {.white-box}
`r cat(' ')`
::::::

::::::::: {.section-box}
**Related Risks**
```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
if(length(rel_risk_risk_item$risk_no) > 0) {
  kbl(select(rel_risk_risk_item, related_risk_link, RELATED_RISK_CONCERN),
      col.names = c("Number", "Description")) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", 
                                        "responsive"),
                  full_width = TRUE, 
                  position = "left") %>%
    column_spec(1, width = "10em")
} else {
  cat(" No related risks.")
}
```

:::::::::


:::::: {.white-box}
`r cat(' ')`
::::::

:::::::::::: {.section-box}
**Response Plan**

::::::::: {.section-box}
**Related Actions**
```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
if(length(rel_risk_action_item$risk_no) > 0) {
  kbl(select(rel_risk_action_item, action_no_link, ACTION),
      col.names = c("Number", "Description")) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", 
                                        "responsive"),
                  full_width = TRUE, 
                  position = "left") %>%
    column_spec(1, width = "10em")
} else {
  cat(" No related actions.")
}
```

:::::::::

:::::: {.white-box}
`r cat(' ')`
::::::

::::::::: {.section-box}
**Related Decisions**

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
if(length(rel_risk_dec_item$risk_no) > 0) {
  kbl(select(rel_risk_dec_item, decision_no_link, DECISION),
      col.names = c("Number", "Description")) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", 
                                        "responsive"),
                  full_width = TRUE, 
                  position = "left") %>%
    column_spec(1, width = "10em")
} else {
  cat(" No related decisions.")
}
```

:::::::::  

<!-- End Response Plan -->
::::::::::::  

<!-- End Risk Item -->
:::::::::::::: 

:::::: {.white-box}
`r cat(' ')`
::::::
